### 2022-11-28 ms.rmd
Fixed a few things and checks the posterios are matching the real data..which they are. We nee dto dos ome cross validation now - maybe drop one species, impute it and compare it to it's real data. Do this for each species.

# Extract the estimated / imputed Z for each species, but drop internal ancestral nodes
  z_blups <- sol[, grep("traittdt_z.animal", colnames(sol))]
  z_blups <- z[,-grep("Node", colnames(z))]
  head(z_blups)

# Remember that these are BLUPs. They are deviations from the intercept. So, to get back to the z we need to add the intercept to each of them.
  z <- z_blups + mean(sol[, "traittdt_z"])

@@

# Have a look at how well the model gets the actual data correct.
  z_known <- data %>% filter(!is.na(tdt_z)) %>% dplyr::select(species, tdt_z) %>% distinct()
    z_est <- apply(z, 2, function(x) median(x))[which(names(z_est) %in% z_known$species)]

>>>>

# Extract the estimated / imputed Z for each species, but drop internal ancestral nodes
  z_blups <- sol[, grep("traittdt_z.animal", colnames(sol))]
  z_blups <- z_blups[,-grep("Node", colnames(z_blups))]
  head(z_blups)

# Remember that these are BLUPs. They are deviations from the intercept. So, to get back to the z we need to add the intercept to each of them.
  z <- z_blups + sol[, "traittdt_z"]

@@

# Have a look at how well the model gets the actual data correct.
  z_known <- data %>% filter(!is.na(tdt_z)) %>% dplyr::select(species, tdt_z) %>% distinct()
    z_est <- apply(z, 2, function(x) median(x))
    z_est <- z_est[which(colnames(z) %in% z_known$species)]
    z_est <- data.frame(z_est)
    z_est$species <- row.names(z_est)
  check_z <- left_join(z_known, z_est, by = "species")
